---
title: "EXP3 pilot, version 3 (invested effort)"
output: 
  html_document:
    df_print: kable
params:
# nelLa prossima riga inserosci il numero del soggetto.
  subj_id: '20'
---

# Subject ``r params$subj_id``

Abbreviations:

* *neg*, *pos*, *scr*: negative, positive, and scrambled faces, respectively
* *stim.near*, *stim.far*: position of the target (red ball) with respect to the face stimulus (*stim.near* = near the face stimulus)
* *EXR*, *RLX*: level of invested effort (EXR=max, RLX=min)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, comment="")

library(rprime)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(rstatix)
library(knitr)
library(pander)
```

```{r preprocessing}
# nelLa prossima riga seleziona la cartella del soggetto. Non devi cmabiare niente
setwd(paste("mPFE3_", params$subj_id, sep = ""))
my_file <- paste("PFE_exp3_faces_fMRI_duplicaSchermo_invertiti-", params$subj_id, "-1.txt", sep ="")

experiment_lines <- read_eprime(my_file)
experiment_data <- FrameList(experiment_lines)

just_level_3 <- keep_levels(experiment_data, 3)
#preview_levels(just_level_3)

df0 <- to_data_frame(just_level_3)

df1 <- df0 %>%
  select(Eprime.LevelName, stimL, valence, correctResp,
         condition, TipoBlocco, Posizione, BloccoN,
         Cycle, Sample, risp.RT, risp.RESP)

names(df1) <- c(
  "stim.idx.local", "stim.name", "valence", "resp.required", 
  "condition", "effort", "target.pos", "block", 
  "run", "stim.idx.global", "RT", "resp.issued")

df1$stim.idx.local <- rep(1:112, 4)
df1$stim.name <- factor(df1$stim.name)
df1$valence <- factor(df1$valence)
df1$resp.required <- factor(df1$resp.required, 
                            labels = c("no", "yes"))
df1$condition <- factor(df1$condition)
df1$effort <- factor(df1$effort)
df1$target.pos <- factor(df1$target.pos, 
                         levels = c("V", "L", "F"),
                         labels = c("stim.near", "stim.far", "foil"))
df1$block <- factor(df1$block)
df1$run <- factor(df1$run)
df1$stim.idx.global <- as.numeric(df1$stim.idx.global)
df1$RT <- as.numeric(df1$RT)
df1$RT[df1$RT == 0] <- NA
df1$RT <- df1$RT + 100
df1$resp.issued <- factor(df1$resp.issued, 
                          labels = c("no", "yes"))
```

## Number of correct responses

```{r correct_responses_plot, fig.width=5, fig.height=3}
df1_correct <- df1 %>%
  filter(resp.required == "yes" & resp.issued == "yes" & target.pos != "foil") %>%
  droplevels(except = c("valence", "effort"))
table_correct <- with(df1_correct, table(effort, valence, target.pos))

ggplot(as.data.frame(table_correct), aes(x = target.pos, y = Freq)) +
  geom_bar(
    aes(fill = valence), stat = "identity", color = "white",
    position = position_dodge(0.9)) +
  facet_wrap(~ effort) +
  fill_palette("jco")
ftable(table_correct)
```

## Number of errors of omission

```{r omit_errors_plot, fig.width=5, fig.height=3}
df1_err_omit <- df1 %>%
  filter(resp.required == "yes" & resp.issued == "no"  & target.pos != "foil")  #%>%
  #droplevels(except = c("valence", "effort")) # Commenta se non ci sono omissioni
table_err_omit <- with(df1_err_omit, table(effort, valence, target.pos))

ggplot(as.data.frame(table_err_omit), aes(x = target.pos, y = Freq)) +
  geom_bar(
    aes(fill = valence), stat = "identity", color = "white",
    position = position_dodge(0.9)) +
  facet_wrap(~ effort) +
  fill_palette("jco")
ftable(table_err_omit)
```

## Number of errors of commission

```{r commit_errors_plot, fig.width=5, fig.height=3}
df1_err_commit <- df1 %>%
  filter(resp.required == "no" & resp.issued == "yes")
table_err_commit <- with(df1_err_commit, table(effort, valence, target.pos))

ggplot(as.data.frame(table_err_commit), aes(x = target.pos, y = Freq)) +
  geom_bar(
    aes(fill = valence), stat = "identity", color = "white",
    position = position_dodge(0.9)) +
  facet_wrap(~ effort) +
  fill_palette("jco")
ftable(table_err_commit)
```

```{r summary_stats}
# Remove scr trials
df1_correct_noscr <- df1_correct %>%
  filter(valence != "scr") %>%
  droplevels()

# Summary stats for each cell
rt_summary_stats <- df1_correct_noscr %>%
  group_by(effort, target.pos, valence) %>%
  get_summary_stats(RT, type = "mean_ci")

rt_temp <- rt_summary_stats
rt_temp$subj <- paste("mPFE3_", params$subj_id, sep = "")
rt_summary_stats_print <- data.frame(rt_temp$subj, rt_temp$valence, rt_temp$effort, rt_temp$target.pos, rt_temp$mean, rt_temp$ci)
out_dir <- paste("/Users/Riccardo/Desktop/analisi_comportamentali/mPFE3_", params$subj_id, "/mPFE3_", params$subj_id, "_results.csv", sep = "")
write.csv(rt_summary_stats_print, out_dir, row.names = FALSE)
```

# Response times (correct trials only)

```{r, rt_boxplot, fig.width=5, fig.height=3}
# Boxplots
rt_barplot <- ggboxplot(
  df1_correct_noscr, x = "target.pos", y = "RT", 
  color = "valence", palette = "jco", facet.by = "effort")
  #title = "Response times (correct responses)")
rt_barplot
```

```{r, rt_interplot, fig.width=5, fig.height=3}
# Interaction plots
rt_interplot <- df1_correct_noscr %>% 
  ggplot() +
  aes(x = target.pos, color = valence, group = valence, y = RT) +
  stat_summary(fun = mean, geom = "point") +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = .1) + facet_wrap(~ effort)
rt_interplot
```

## Outliers

```{r outliers, fig.width=5, fig.height=3}
# Identify outliers
df1_correct_noscr %>%
  select(-c(stim.idx.local, stim.name, resp.required,
            condition, stim.idx.global, resp.issued)) %>%
  group_by(effort, target.pos, valence) %>%
  identify_outliers(RT) %>%
  print.data.frame()
```

## Normality check (Shapiro-Wilk)

```{r, fig.width=3, fig.height=3}
# Normality assumption
rt_lm  <- lm(RT ~ effort * target.pos * valence, 
             data = df1_correct_noscr)
# Create a QQ plot of residuals
ggqqplot(residuals(rt_lm))
# Compute Shapiro-Wilk test of normality
```

```{r}
shapiro_test(residuals(rt_lm))
```

## Cell-wise normality check (Shapiro-Wilk)
```{r}
# Check normality assumption by group
df1_correct_noscr %>%
  group_by(effort, target.pos, valence) %>%
  shapiro_test(RT)
```

## Cell-wise QQplot for each cell

```{r, fig.height=7, fig.width=4}
ggqqplot(df1_correct_noscr, "RT", ggtheme = theme_bw()) +
  facet_grid(valence + target.pos ~ effort, labeller = "label_both")
```

## Homogeneity of variance

```{r}
# Homogeneity of variance
df1_correct_noscr %>% levene_test(RT ~ valence * target.pos * effort)
```

## ANOVA on RTs

```{r anova}
rt.aov <- df1_correct_noscr %>% anova_test(RT ~ valence * target.pos * effort)
```

```{r anova_table}
pander(rt.aov)
```

```{r rt_summary_stats, results = 'asis'}
pander(rt_summary_stats)
```



